### 2010-03-31 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: clarify the situation of SYB.

Interestingly, our generic induction principle allows a programming
style reminiscent to the Scrap Your Boilerplate~\cite{spj:syb} (SYB)
approach. Like SYB, we provide a generic operator to manipulate and
carry operations over data-types. However, unlike SYB, we do not need
support from the compiler, as required by the $\CN{Typeable}$
class. Indeed, in our setting, data-types are reflected in the
language, hence our ability to manipulate them directly.

>>>>

Another generic programming framework is Scrap Your
Boilerplate~\cite{spj:syb} (SYB). Our proposal is different in various
ways. The corner stone of SYB is the \emph{spine} view of data-type
constructors. A data-type is a spine composed by a constructor applied
to some arguments. Further, this spine is equipped with some
combinators including, primarily, an iterator. In this setting,
generic programs are written by composing these combinators. This
relies on a $\CN{Typeable}$ type-class, allowing dynamic dispatch to
data-type specific operations. As a result, SYB is not reflexive: it
is restricted to data-types instanciating $\CN{Typeable}$. Moreover,
it forbids type-indexed data types: it can only define generic
functions.
